---
title: "Course Project 1"
author: "Rick van Zijl"
date: "29 januari 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data


```{r}
setwd("C:/")
data <- read.table("activity.csv", header = TRUE, sep = ',')
summary(data)
```

## What is mean, median and histogram of steps taken per day?

```{r}
StepsTotal <- aggregate(steps ~ date, data = data, sum, na.rm = TRUE)
mean(StepsTotal$steps, na.rm = TRUE)
median(StepsTotal$steps, na.rm = TRUE)
hist(StepsTotal$steps)

```

## Timeseries Plot of the average number of steps

```{r}
library(dplyr)
library(ggplot2)
TimeSeries <- data %>% group_by(interval) %>% summarise(Average = mean(steps, na.rm = TRUE))
T <- ggplot(TimeSeries, aes(y = Average, x = interval)) + geom_line()
print(T)
```

## The 5-minute interval that, on average, contains the maximum number of steps
```{r}
TimeSeries[TimeSeries$Average == max(TimeSeries$Average),]
```

## Code to describe and show a strategy for imputing missing data
## Histogram of the total number of steps taken each day after missing values are imputed

```{r}
data$steps[is.na(data$steps)] <- mean(TimeSeries$Average)
StepsTotal <- aggregate(steps ~ date, data = data, sum, na.rm = TRUE)
hist(StepsTotal$steps)
```

## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r}
data$day <- weekdays(as.Date(data$date))
data$day <- ifelse(data$day == "zaterdag", "Weekend", ifelse(data$day == "zondag", "Weekend", "Workingday"))
TimeSeries <- data %>% group_by(interval, day) %>% summarise(Average = mean(steps, na.rm = TRUE))
ggplot(TimeSeries, aes(y = Average, x = interval)) + geom_line() + facet_grid(. ~ day)

```
